%************************************************
\chapter{Discussion}\label{ch:discussion}
%************************************************

\section{Contributions}
My work has improved PGF, at least a bit


Issue with the suggestion algorithm, cannot take more than one word..

\section{To dos}
How we add a special behavior of names with spaces in it.
Write about how we get the most related results by counting names
Write that we use fuzzy search
Write how to install GF
Write about how we remove sentences like people who know java and who know java
Fördelar med att använda Solr framför ett gigantiskt lexikon (we get fuzzy search and keyword only suggestions, maybe faster too and more flexible)
Write about how GF actually works, parsing and linearization


Add "more sophisticated suggestion engine with graph database. Eg. if one type "people" then it shall recognize it as a node and check all distinct edges from that node as relationships to other nodes and suggest to autocomplete all those nodes.
\section{Negative things}
Generates three trees for each instruction (p "people who know Java or Python and who work in London"
Can just generate all instructions in all languages and add them to solr. No need for translating then.
Generates the instruction "people who know Skill0 and who work in Location0" but also "people who work in Location0 and who know Skill0" they're equivalent.
Write about how the suggestions are not optimal.

\section{install the environment}
Prereqs: Tomcat8, Maven. Install GF through cabal (needed to generate instructions). Write howto install generate instructions and mock data. Write how to add the gf.pgf.jar as a maven dependency

mvn install:install-file -Dfile=org.grammaticalframework.pgf.jar -DgroupId=org.grammaticalframework -DartifactId=pgf -Dversion=1.0 -Dpackaging=jar

\section{Issues}
Bug causes gf to parse strings into multiple ASTS and multiple linearizations, and the application post process alot.
Must have capital letter on each name
projects who use Java is an incorrect sentence. It shall be projects which/that use Java. The suggestion algorithm does not search for names that contains more than one word, it only use one word at a time.

\section{Future work}
Speech to text
Handle ambiguous instructions
Make application know which language that is used
Use prediction function in pgf to give suggestions of sentences (\url{https://groups.google.com/forum/#!topic/gf-dev/uoQDQODSzoo})
    I thought about one approach: As we still want to have keyword only suggestions we can implement a "backward completion function" by mapping each word with all other words that can be used in front of it.
    When we have the first word we can use the completion function in PGF. This solution would make it possible to suggest a sentence based on a sentence.
Instead of storing the names in solr, store them as a lexicon in GF (maybe)
Not use RGL, instead use string concatenation, since we only support a few sentences

Support more variations of questions 

\section{Related work}
