%*******************************************************
% Acknowledgments
%*******************************************************
\pdfbookmark[1]{Acknowledgments}{acknowledgments}

\vspace{30mm}
\begin{flushleft}{\slshape

We have seen that computer programming is an art, because it applies accumulated knowledge to the world, because it requires skill and ingenuity, and especially
    because it produces objects of beauty. A programmer who
    subconsciously views himself as an artist will enjoy what he does and will do it better.} \medskip
\end{flushleft}
\begin{flushright}
--- \defcitealias{knuth:1974}{Donald E. Knuth}\citetalias{knuth:1974} \citep{knuth:1974}
\end{flushright}



\bigskip

\begingroup
\let\clearpage\relax
\let\cleardoublepage\relax
\let\cleardoublepage\relax
\chapter*{Acknowledgments}
I want to thank my supervisor Krasimir Angelov for his guidance throughout the whole project. He has always showed great interest in my work from the very beginning until the end. 

I also want to thank the whole Findwise organization, where I did most of the programming work. In particular, a special thanks to Svetoslav Marinov who came up with the project idea. Also a special thanks to Per Fredelius who was my advisor at Findwise. Per inspired me with many ideas to the project. 
\newline
\newline
As this thesis ends the academic part of my life, I also want to thank other people who have helped me during my time as a student.
\newline
\newline
I want to thank my friends in Monaden\footnote{The lunchroom for computer science students at University of Gothenburg} and in Hilbert\footnote{The lunchroom for physics students at University of Gothenburg}. Their company and help have been invaluable.
\newline
\newline
Finally, I want to thank my family and my girlfriend Nellie for always supporting and believing in me. I wouldn't be where I am now if it weren't for them.
\newline
\newline
\newline
\newline
\textbf{Thank you!}
\newline
\newline
---
\newline
Martin Agfjord
\newline
Gothenburg, \today
\endgroup



