\bibliographystyle{sltc2014}
%\bibliography{sltc2014} 

\begin{thebibliography}{}

\bibitem[\protect\citename{Li}2013]{li:2013}
X.~Li.
\newblock 2013.
\newblock {{Under the Hood: The natural language interface of Graph Search}}.
\newblock URL: https://www.facebook.com/notes/facebook-engineering/under-the-hood-the-natural-language-interface-of-graph-search/10151432733048920 [Online; accessed 23-July-2014].

\bibitem[\protect\citename{Ranta}2013]{ranta:2013}
A.~Ranta.
\newblock 2013.
\newblock {{Grammatical Framework: Programming with Multilingual Grammars}}.
\newblock CSLI Publications, Stanford, 2011.
\newblock ISBN-10: 1-57586-626-9 (Paper), 1-57586-627-7 (Cloth).

\bibitem[\protect\citename{Kuć}2011]{kuc:2011}
R.~Kuć.
\newblock 2011.
\newblock {{Apache Solr 3.1 cookbook}}.
\newblock Packt Publishing, 2011.
\newblock ISBN-13: 978-1849512183 (Paper).

\bibitem[\protect\citename{Megyesi \bgroup et al.\egroup }2008]{m+-08}
B.~Megyesi, B.~Dahlqvist, E.~Pettersson, S.~Gustafson-Capkov\'a, and J.~Nivre.
\newblock 2008.
\newblock Supporting research environment for less explored languages: A case
  study of {S}wedish and {T}urkish.
\newblock In J.~Nivre, M.~Dahll\"of, and B.~Megyesi, editors, {\em Resourceful
  Language Technology: Festschrift in Honor of Anna S\aa{}gvall Hein}, Studia
  Linguistica Upsaliensia 7, pages 96--110. Acta Universitatis Upsaliensis.

\bibitem[\protect\citename{Stymne}2008]{s-08}
S.~Stymne.
\newblock 2008.
\newblock German compounds in factored statistical machine translation.
\newblock In A.~Ranta and B.~Nordstr\"om, editors, {\em Proceedings of GoTAL,
  the 6th Interonational Conference on Natural Language Processing}, pages
  464–--475, Gothenburg, Sweden. Springer.

\bibitem[\protect\citename{Wierzbicka}1987]{w-87}
A.~Wierzbicka.
\newblock 1987.
\newblock {\em English Speech Act Verbs: A semantic dictionary}.
\newblock Academic Press, Sidney.


\end{thebibliography}